05_DESeq_manipulation

### 2019-06-16 analysis/05_DESeq2_manipulate.Rmd
new pcs
mostly good, not heatmap
work in progress

```{r candidates}
plotcandidates(dds.female_hypothalamus, "female hypothalamus")
plotcandidates(dds.female_pituitary, "female pituitary")
plotcandidates(dds.female_gonad, "female gonad")
plotcandidates(dds.male_hypothalamus, "male hypothalamus")
plotcandidates(dds.male_pituitary, "male pituitary")
plotcandidates(dds.male_gondad, "male gonad")
```

>>>>

## candidate genes

```{r candidates}
plotcandidates(dds.female_hypothalamus, "female hypothalamus")
plotcandidates(dds.female_pituitary, "female pituitary")
plotcandidates(dds.female_gonad, "female gonad")
plotcandidates(dds.male_hypothalamus, "male hypothalamus")
plotcandidates(dds.male_pituitary, "male pituitary")
plotcandidates(dds.male_gondad, "male gonad")

```
